README.md

### 2020-11-12 README.Rmd
accepted version 🏔️

Please cite this repository as `The seed germination spectrum of alpine plants: a global meta-analysis. Manuscript in preparation.`

>>>>

Please cite this repository as:

> Fernández-Pascual E, Carta A, Mondoni A, Cavieres L, Rosbakh S, Venn S, Satyanti A, Guja L, Briceño VF, Vandelook F, Mattana E, Saatkamp A, Bu H, Sommerville K, Poschlod P, Liu K, Nicotra A, Jiménez-Alfaro B (2020) The seed germination spectrum of alpine plants: a global meta-analysis. *New Phytologist*.
